% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=1in,right=1in,top=.75in,bottom=.75in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{fancyhdr}
\pagestyle{fancy}
%\renewcommand{\headrulewidth}{0.4pt}% Default \headrulewidth is 0.4pt
%\fancyfoot[LO,R]{A Bibliography of Ægypt by John Crowley}
%\fancyfoot[R]{\thepage}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={A Bibliography of Ægypt by John Crowley},
  pdfauthor={Compiled by Brian Murphy},
  hidelinks
}
  
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{\hruleafter}
\titleformat{\subsection}
  {\normalfont\large\bfseries}{\thesubsection.}{1em}{}
\titleformat{\paragraph}
  {\normalfont\normalsize\itshape}{\thesubsubsection.}{1em}{}

\newcommand{\hruleafter}[1]{#1\hrule}


\title{A Bibliography of Ægypt by John Crowley}
\author{Compiled by Brian Murphy}
\date{09/09/2024}

\begin{document}
%%\frontmatter
{\let\cleardoublepage\clearpage 
\maketitle
%%\tableofcontents
}

%%\mainmatter
\section{Introduction}\label{introduction}

The goal is to list all of the books and authors mentioned throughout \emph{Ægypt}, or \emph{The Solitudes}, by chapter. A complete list of those authors are listed at the end in alphabetical order by the first name. If a chapter is missing below, then it likely did not have any books or authors mentioned within it. Books listed in \textbf{bold} are fictional works created by Crowley, at least to the best of my estimation. The \emph{Authors Mentioned} subsections list authors that were mentioned within a chapter but did not mention a particular book.

In most cases I tried to cite a work that would have been appropriate for the timeframe of the story in which it is mentioned. In some cases, I have not been able to find a suitable edition and so cite a modern edition instead. Those will eventually be cleaned up to reflect either a copy of the work from the 16th century, one up to the 1978, or one available to Crowley while he was writing as I find them.

Future updates will likely provide citations for when a particular author is mentioned within the text. I'm not likely to do this any time soon, however. Eventually, I will add in subsequent books in the series, but I'm in no real hurry to do so. This was purely a fun side-project that got my head away from ``Real Life'' for a time.

I'm open to any ideas as to how this can be updated and expanded. For any corrections or comments the reader can email me directly at \href{mailto:murfman@pm.me}{\nolinkurl{murfman@pm.me}}.

Special Thanks goes to the guys within the \href{https://discord.com/channels/460145057975238714/474725139297337367}{\textsc{\#Books}} channel on \href{https://www.mu-podcast.com/}{\textsc{The Miskatonic University Podcast}} \href{https://discord.com/channels/460145057975238714/}{\textsc{Discord Server}}. You guys know who you are.

\bigskip 

\emph{(This is still, and likely will remain, a work in progress.)}

\pagebreak 
\section{Author's Note}\label{authors-note}

\paragraph{Books Mentioned:}\label{books-mentioned}

\begin{itemize}
\tightlist
\item
  Walter Scott. \emph{Hermetica}.
\item
  Luis de Góngora, trans. Cunningham, Gilbert P. \emph{Soledades}.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned}
Joseph Campbell, Elizabeth L. Eisenstein, Mircea Eliade, Peter French, Hans Jonas, Frank E. \& Fritz P. Manuel, Giorgio di Santillana, Stephen Schoenbaum, Wayne Shumaker, Keith Thomas, Lynn Thorndike, D. P. Walker, Dame Francis Yates, John Mitchell, Katerine Maltwood, Robert Graves, Lois Rose, Richard Deacon, Walter Scott, Luis de Góngora.

\section{The Prologue on Earth}\label{the-prologue-on-earth}

\paragraph{Books Mentioned:}\label{books-mentioned-1}

\begin{itemize}
\tightlist
\item
  Bruno, Giordano. \emph{De monade, numero et figura}. 1961.
\end{itemize}

\section{Vita}\label{vita}

\subsection{One}\label{one}

\paragraph{Books Mentioned:}\label{books-mentioned-2}

\begin{itemize}
\tightlist
\item
  De Góngora Y Argote, Luis. \emph{The Solitudes of Luis De Góngora}. 1968.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-1}

Peter Ramus

\subsection{Two}\label{two}

\paragraph{Books Mentioned:}\label{books-mentioned-3}

\begin{itemize}
\tightlist
\item
  \textbf{Kraft, Fellowes. \emph{Darkling Plain}.}
\item
  Burnett, Frances Hodgson, and Sue Ullstein. \emph{The Secret Garden}. Longman Publishing Group, 1975.
\item
  \textbf{Norton, Mary. \emph{The Borrowers Abroad}.}\footnote{There is no novel by Norton titled~\emph{The Borrowers Abroad}. This may have been deliberate by Crowley, or an accident, since all of the books are named in a similar pattern (i.e.~\emph{The Borrowers Afield},~\emph{The Borrowers Afloat},~\emph{The Borrowers Afield},~\emph{The Borrowers Avenged}. More research could be done to see if this was a proposed title of another book in the series, or if this was a subtle way to shift the book away from the reality, or history in this case, that we experience as the reader.)}
\item
  \textbf{Kraft, Fellowes. \emph{Under Saturn, A Novel of Wallenstein}}\footnote{Seems to be based on the biography of Wallenstein: Watson, Francis.~\emph{Wallenstein, Soldier Under Saturn}. 1969.}
\item
  \textbf{Kraft, Fellowes. \emph{Bitten Apples}}
\end{itemize}

\subsection{Three}\label{three}

\paragraph{Books Mentioned:}\label{books-mentioned-4}

\begin{itemize}
\tightlist
\item
  De Góngora Y Argote, Luis. \emph{The Solitudes of Luis De Góngora}. 1968.\footnote{Crowley quotes Cunningham's translation of the First Solitude lines 94-96 and then 108-111, then 112-116. Then he switches to the original Spanish for pieces of lines 113-114, and then again the Spainish for lines 119-121.}
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-2}

Lady Mary Wortley Montagu, Luis de Góngora, Percy Bysshe Shelley

\subsection{Four}\label{four}

\paragraph{Books Mentioned:}\label{books-mentioned-5}

\begin{itemize}
\tightlist
\item
  Barr, Frank Walker. \emph{Time's Body}.
\item
  \textbf{Barr, Frank Walker. \emph{Mythos and Tyrannos}.}
\item
  \emph{Seven Sobs of a Sorrowful Soule for Sinne}. 1597.
\item
  Shakespeare, William. \emph{Measure for Measure}. Cambridge UP, 2006.
\item
  \emph{Unknown Volumes of Encyclopedia Britannica}. 1939.\footnote{I am assuming the 1939 edition since Pierce mentions bringing several volumes of this fictitious version with him to Blackberry Jams.}
\item
  Malory, Thomas, and Sidney Lanier. \emph{The Boy's King Arthur: Being Sir Thomas Malory's History of King Arthur and His Knights of the Round Table}. 1921.
\item
  \textbf{Kraft, Fellowes. \emph{Bruno's Journey}. 1931}
\end{itemize}

\subsection{Five}\label{five}

\paragraph{Books Mentioned:}\label{books-mentioned-6}

\begin{itemize}
\tightlist
\item
  Virgil. \emph{Virgil's Eclogues}. University of Pennsylvania Press. 2011.\footnote{Line 6, ``Iam redit et Virgo, redeunt Saturnia regna'' ``The virgin reappears and Saturn reigns'' https://la.wikisource.org/wiki/Eclogae\_vel\_bucolica/Ecloga\_IV.}
\item
  Dante. \emph{Divine Comedy}. Modern Library. 1950
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-3}

Homer, Sophocles, Dante, Shakespeare, Cervantes

\subsection{Six}\label{six}

\paragraph{Books Mentioned:}\label{books-mentioned-7}

\begin{itemize}
\tightlist
\item
  \textbf{Rose, Lois. \emph{Steganography}.}
\item
  Bates, Lizzie. \emph{Stories of the Flowers}. 1872.
\item
  Perlesvaus. \emph{The High History of the Holy Graal}. 1898.
\item
  Sprat, Thomas. \emph{The History of the Royal Society of London, for the Improving of Natural Knowledge}. 1667.
\item
  Frazer, James George. \emph{The Golden Bough: A Study in Magic and Religion}. 1932.
\item
  Longfellow, Henry Wadsworth. \emph{The Golden Legend}. 1878.
\item
  Apuleius. \emph{The Golden Ass}. Penguin UK, 1998.
\item
  Hyginus. \emph{Poeticon Astronomicon}. 1502.
\item
  Huizinga, J. \emph{The Waning of the Middle Ages: A Study of the Forms of Life, Thought and Art in France and The Netherlands in the XIVth and XVth Centuries}. Pickle Partners Publishing, 2016.
\item
  Burgess, Thornton W. \emph{Old Mother West Wind}. Courier Corporation, 2012.\footnote{Mentioned by Crowley as ``Old Mother Westwind''}
\item
  Miss Martha's History Book\footnote{A completely unnamed history book belonging to Miss Martha, Pierce's uncle Sam's Houskeeper.}
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-4}

Giambattista Vico, Grimm, Frobenius, George Santayana, Giorgio di Santillana, Anthony Trollope

\subsection{Seven}\label{seven}

\paragraph{Books Mentioned:}\label{books-mentioned-8}

\begin{itemize}
\tightlist
\item
  Shakespeare, William. \emph{Shakespeare's King Henry VIII}. 1912.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-5}

Æneas.

\section{Lucrum}\label{lucrum}

\subsection{One}\label{one-1}

\paragraph{Books Mentioned:}\label{books-mentioned-9}

\begin{itemize}
\tightlist
\item
  Sidney, Phillip, Sir. \emph{The Lady of May}. 1598.
\item
  Holinshed, Raphael. \emph{Holinshed's Chronicals: Richard II, 1398-1400, Henry IV and Henry V.} 1923.
\item
  Monardes, Nicolás. \emph{Joyfull Newes Out of the Newe Founde Worlde}. Walter J. Johnson Incorporated, 1970.
\item
  Plutarch and North, Thomas, Sir. \emph{Lives. Englished}. London Dent. 1894.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-6}

Aeschylus, Euripides, Leland, Polydore Virgil, Charles Dickens, Sir Walter Scott.

\subsection{Three}\label{three-1}

\paragraph{Books Mentioned:}\label{books-mentioned-10}

\begin{itemize}
\tightlist
\item
  Trithemius, Johann. \emph{Johannis Trithemii \ldots{} Steganographia\ldots Illustrata a Wolfgango Ernesto Heidel}. 1676.
\item
  Dee, John. \emph{Propædeumata Aphoristica Ioannis Dee, Londinensis, De Præstantioribus Quibusdam Naturæ Virtutibus}. 1568.
\item
  \textbf{\emph{Talbot's Unnamed Enochian Manuscript}}\footnote{Crowley mentions that ``Talbot'' aka Edward Kelley ``It was a manuscript on thick parchment, narrow and sewn up with heavy greased black thread. There was no cover or binding. The characters it was written in started immediately at the top of the first page without any heading, as though this were perhaps not the first page at all. Doctor Dee picked up the lamp and bent close over the page. Mr.~Talbot turned the heavy worm-holed leaf. The second page was the same: a solid block of characters from top to bottom. It is in a cipher, the doctor said. I can read a cipher, if it hides a language that I know.''}
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-7}

Gerardus Mercator, Tycho Brahe.

\subsection{Four}\label{four-1}

\paragraph{Books Mentioned:}\label{books-mentioned-11}

\begin{itemize}
\tightlist
\item
  Mead, G.R.S. \emph{Thrice-greatest Hermes}. London and Benares. 1906.
\item
  Beeson, Charles H. ``A History of Magic and Experimental Science During the First Thirteen Centuries of Our Era. Lynn Thorndyke.'' \emph{Classical Philology}, vol.~20, no. 2, Apr.~1925, pp.~163--67. https://doi.org/10.1086/360664.
\item
  Bruno, Giordano. \emph{Opera Omnia}. 1854.
\item
  ---. \emph{Jordani Bruni Opera Latine Conscripta}. 1962.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-8}

Giordano Bruno, Copernicus, Galileo Galilei, Thomas Aquinas, Dante, Aristotle, Hermes Trismegistus, Cicero, Lactantius, Plato, Virgil, Pythagoras, Plotinus, Jean-François Champollion, E. A. Wallis Budge. Margaret Mead, Aleister Crowley, Martin del Rio ``Delrio,'' Johannes Kepler, René Descartes, Francis Bacon, Isaac Newton, Proclus, Iamblichus, Paracelsus.

\subsection{Five}\label{five-1}

\paragraph{Books Mentioned:}\label{books-mentioned-12}

\begin{itemize}
\tightlist
\item
  \textbf{Kraft, Fellowes. \emph{The Court of Silk and Blood}.}
\item
  \textbf{---. \emph{A Passage at Arms}.}
\item
  Unnamed \emph{Nancy Drew Mystery Stories} Novel.
\item
  Unnamed \emph{Mr.~Moto} novel by John P. Marquand.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-9}

Giordano Bruno, Agrippa (unsure which one), Gerolamo Cardano, John Galsworthy.

\subsection{Six}\label{six-1}

\paragraph{Books Mentioned:}\label{books-mentioned-13}

\begin{itemize}
\tightlist
\item
  \emph{TV Guide}.
\item
  \textbf{\emph{Faraway Crier}.}
\item
  \textbf{Kraft, Fellowes. \emph{Sit Down, Sorrow}.}\footnote{A memoir of Fellowes Kraft.}
\end{itemize}

\subsection{Seven}\label{seven-1}

\paragraph{Books Mentioned:}\label{books-mentioned-14}

\begin{itemize}
\tightlist
\item
  Seneschal, Jean Le, and Gaston Raynaud. \emph{Les Cent Ballades\,: Poème Du XIV{[}E{]} Siècle}. 1905, p221.
\item
  \emph{The Eighteenth Brumaire of Louis Bonaparte}, Charles H. Kerr, Chicago, 1907.\footnote{``Hegel says somewhere that all great historic facts and personages recur twice. He forgot to add:''Once as tragedy, and again as farce.'' Caussidiere for Danton, Louis Blanc for Robespierre, the ``Mountain'' of 1848-51 for the. ``Mountain'' of 1793-95, the Nephew for the Uncle. The identical caricature marks also the conditions under which the second edition of the eighteenth Brumaire is issued.''}
\item
  \textbf{\emph{Phaeton's Car}.}\footnote{Fictitious book apparently a play on Francis Bacon's~\emph{Of Vicissitude of Things}~``Phaeton's car went but a day: and the three years drought in the time of Elias, was but particular, and left people alive.'' Para. 60.}
\item
  \textbf{\emph{Worlds in Division}.}
\item
  \textbf{\emph{Dawn of the Druids}.}
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-10}

Karl Marx.

\subsection{Eight}\label{eight}

\paragraph{Books Mentioned:}\label{books-mentioned-15}

\begin{itemize}
\tightlist
\item
  Lanier, Sidney and Wyeth, N. C., Illustrator. \emph{The Boy's King Arthur. Scribner's Illustrated Classics. Sir Thomas Malory's History of King Arthur and His Knights of the Round Table}. Charles Scribner's Sons. 1937.
\item
  Briggs, Austin. \emph{Flash Gordon}. 1940-1948.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-11}

Rablelais.

\section{Fratres}\label{fratres}

\subsection{Two}\label{two-1}

\paragraph{Books Mentioned:}\label{books-mentioned-16}

\begin{itemize}
\tightlist
\item
  \emph{New York Times}.
\item
  \textbf{\emph{Phaeton}'\emph{s Car}.}\footnote{Fictitious book apparently a play on Francis Bacon's~\emph{Of Vicissitude of Things}~``Phaeton's car went but a day: and the three years drought in the time of Elias, was but particular, and left people alive.'' Para. 60.}
\item
  \textbf{Niblick, Helen. \emph{The Way's Far Turning}.}
\item
  \textbf{Kraft, Fellowes. \emph{The Book of a Hundred Chapters}.}
\item
  \emph{Dictionary of National Biography}. 1961.
\item
  Benians, Ernest Alfred. \emph{The Cambridge Modern History}. Cambridge\,: UP, 1907.
\item
  Herbermann, Charles George. \emph{The Catholic Encyclopedia: An International Work of Reference on the Constitution, Doctrine, Discipline, and History of the Catholic Church}. 1908.
\item
  Barr, Franks Walker. Unnamed collected works of histories.
\item
  \emph{Unnamed Bible}.
\item
  Stedman, Joseph F. \emph{My Sunday Missal: Using New Translation From New Testament and a Simplified Method of Following Mass With an Explanation Before Each Mass of Its Theme}. Confraternity of the Precious Blood, 1961.\footnote{Title given in Aegypt is~\emph{Our Sunday Missal}~which could have been a misremembering of Crowley's part, or another slight alteration of the book's world from our own. Either way, this is the closest thing I can see Pierce having on his shelf.}
\item
  Shakespeare, William. \emph{Unknown volumes of the Yale Shakespeare}
\item
  Dee, John. \emph{Monas hieroglyphica}. Antwerp, 1564.
\item
  Thorndike, Lynn. \emph{Four Unnamed Volumes}.\footnote{While the four volumes are not mentioned by name, we can make some guesses as to which they are since they are a part of the ``secondary sources'' mentioned for Pierce's novel. ( i.e.~\emph{The Place of Magic in the Intellectual History of Europe},~\emph{The History of Medieval Europe}, up to any four of the eight volumes of the~\emph{History of Magic and Experimental Science},~\emph{Check-list of Rotographs in the History of Natural and Occult Sciences},~\emph{\href{http://hdl.handle.net/2027/mdp.39015025028716}{*The Sphere of Sacrobosco and its Commentators,*}}, etc. ).}
\item
  \textbf{Sacrobosco, Earl. \emph{Unnamed Astronomy Textbook}.}
\item
  Lewis, Charlton T. \emph{Lewis and Short Latin Dictionary}. 1966.
\item
  Davidson, Gustav. \emph{A DICTIONARY OF ANGELS\,: INCL. THE FALLEN ANGELS}. 1971.\footnote{While this is not named outright and is simply referred to as ``a dictionary of angels'' it is by far the most famous published prior to the 1980s and is likely the one Crowley was referring to.}
\item
  \emph{Unnamed Big Dictionary}.
\item
  \emph{Unnamed Big Picture Book of Clocks}.\footnote{There are a few possibilities here as to what this books could have been. I'm simply going to list the most likely candidates here: ``The Book of Clocks'' by David Thompson (1971), ``Clocks and Watches'' by Eric Bruton (1973), ``The Art of the Clockmaker'' by Tardy (early 1970s), ``The Lore of the Clock'' by G. H. Baillie (1973).}
\item
  \emph{Unknown Volumes of Encyclopedia Britannica}. 1939.\footnote{The Encyclopedia Britannica became the first encyclopedia to undergo continual revisions in 1933. Crowley mentions ``Several volumes of the 1939 edition'' in this chapter, but there was not a specific edition published that year and as such it is impossible to easily tell what volumes of the 1933 14th edition were reprinted during 1939 specifically. Again this could be either intentional by Crowley subtly showing the differences between our world and the book's, or he simply could have chosen a date. Personally, I think it is likely the former.}
\item
  \emph{Unknown Big Shakespeare}.
\item
  \emph{Unknown Big Bible}.
\item
  Murphy, John and et. al.~\emph{The Holy Bible : translated from the Latin Vulgate: \ldots{}} University of Toronto, 1914.\footnote{The Douay-Rheims Bible, sometimes known simply as the Douai Bible was a translation for the Latin Vulgate completed by the English College, Douai in 1582 \& 1609.}
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-12}

Norton, Norris, Nofzinger, Mackenzie, Macauley, Macdonald, Ross Lockbridge, Joseph Lincoln, Shellabarger, Costain, Milton.

\subsection{Three}\label{three-2}

\paragraph{Books Mentioned:}\label{books-mentioned-17}

\begin{itemize}
\tightlist
\item
  \textbf{Kraft, Fellowes. \emph{Bruno's Journey}}\footnote{This was Kraft's first book.}
\item
  \textbf{---. \emph{Under Saturn}.}
\item
  \textbf{---. \emph{Darkling Plain}.}
\item
  Fludd, Robert. \emph{Unnamed book}.\footnote{This can only mean Fludd's~\emph{Utriusque Cosmi}, however, there were no publications in english prior to the late 20th century. I believe it is instead referring to the following, but there will never be a way to tell for certain. (Paracelsus.~\emph{The Hermetic and Alchemical Writings of Aureolus Philippus Theophrastus Bombast, of Hohenheim, Called Paracelsus the Great}. 1894.)}
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-13}

Marsilio Ficino, Robert Fludd.

\subsection{Four}\label{four-2}

\paragraph{Books Mentioned:}\label{books-mentioned-18}

\begin{itemize}
\tightlist
\item
  ``\emph{Death's dream kingdom}''. Unknown Poem.\footnote{This must refer to T. S. Eliot's ``The Hollow Men'' from~\emph{Poems, 1909--1925}~(Faber \& Faber Limited, 1925).}
\item
  \emph{Picatrix: Das Ziel des Weisen von Pseudo-Magriti}, aus dem Arabischen ins Deutsche übersetzt von Hellmut Ritter und Martin Plessner {[}\emph{Picatrix: The Goal of the Wise Man by Pseudo-Magriti}, translated from Arabic into German by Ritter and Plessner{]}. London: Warburg Institute, 1962
\item
  \textbf{Kraft, Fellowes. \emph{Unfinished Final Novel}.}
\end{itemize}

\subsection{Five}\label{five-2}

\paragraph{Books Mentioned:}\label{books-mentioned-19}

\begin{itemize}
\tightlist
\item
  Thomas, Saint. \emph{The ``Summa Theologica'' of St.~Thomas Aquinas}. 1917.
\item
  Magus, Saint Albertus. \emph{Commentaries on The ``Summa Theologica''}.
\item
  ---. \emph{On Sleeping and Being Awake''}.
\item
  ---. \emph{Book of Secrets''}.
\item
  de Sacrobosco, Johannes. \emph{Tractatus de Sphæra}.
\item
  Cecco of Ascoli. \emph{Commentary on the Sphere}.1250.
\item
  Solomon. \emph{Shadows of Ideas}.\footnote{I have no idea what this is referring to.}
\item
  Ficcino, Marsilo. \emph{De vita coelitis comparanda}.
\item
  Horapollo. \emph{Hieroglyphica}. \textasciitilde1419.
\item
  Iambilichus. \emph{On the Mysteries of the Egyptians}.
\item
  Apuleius. \emph{The Golden Ass}. 158-180.
\item
  al-Hakīm, Ghāyat. \emph{Picatrix}.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-14}

Cicero, Quintilian, St.~Albertus Magus, St.~Thomas Aquinas, Aristotle, St.~Jerome, St.~Ambrose, Augustine of Hippo, Lactantias, Horapollo.

\subsection{Six}\label{six-2}

\paragraph{Books Mentioned:}\label{books-mentioned-20}

\begin{itemize}
\tightlist
\item
  \emph{Unnamed Children's Book}.\footnote{I spent way too much time trying to track this book down. As best I can tell, there is no surviving children's ``book about the family of mice who go traveling in a balloon'' that was published in 1978 or before.}
\end{itemize}

\subsection{Seven}\label{seven-2}

\paragraph{Books Mentioned:}\label{books-mentioned-21}

\begin{itemize}
\tightlist
\item
  \emph{Psalms 87 / Hebrew - English Bible / Mechon-Mamre}. \url{mechon-mamre.org/p/pt/pt2687.htm}.
\item
  Ficcino, Marsilio. \emph{Pimander}. 1543.\footnote{Klutstein, Ilana. ``Ficino's Hermetic Translations: English Translation of His Latin Pimander.'' \emph{Huji}, Feb.~2017, www.academia.edu/31423671/Ficinos\_Hermetic\_Translations\_English\_Translation\_of\_His\_Latin\_Pimander.}
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-15}

Cecco of Ascoli, Plato, Aristotle, Pythagoras, Plato, Epicurus, Marsilio Ficino.

\subsection{Eight}\label{eight-1}

\paragraph{Books Mentioned:}\label{books-mentioned-22}

\begin{itemize}
\tightlist
\item
  de Sacrobosco, Johannes. \emph{Tractatus de Sphæra}.
\item
  Bruno, Giordano. \emph{Ars Memoriae}. 1582.{[}\^{}35{]}
\item
  Iambilichus. \emph{On the Mysteries of the Egyptians}.
\item
  Agrippa, Heinrich Cornelius. \emph{De Occulta Philosophia}. 1533
\item
  \emph{ORPHIC HYMNS 1-40 - Theoi Classical Texts Library}. www.theoi.com/Text/OrphicHymns1.html.
\item
  Lull, Ramón. \emph{Ars Magna}. 1501.
\item
  Copernicus, Nicolaus. De Revolutionibus Orbium Coelestium. 1543.
\item
  \emph{Das Nibelungenlied: Song of the Nibelungs}. Yale UP, 2006.
\item
  Malory, Thomas. \emph{Le Morte Darthur: The Winchester Manuscript}. Oxford UP, USA, 1998.
\item
  Spenser, Edmund. \emph{The Faerie Queene}. CUP Archive, 1920.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-16}

Pythagoras, Zoroaster.

\subsection{Nine}\label{nine}

\paragraph{Books Mentioned:}\label{books-mentioned-23}

\begin{itemize}
\tightlist
\item
  Bruno, Giordano. \emph{De umbris idearum}. 1582.
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-17}

Copernicus, Aristotle, Lucretius, Cusanus, Antoine de la Faye.

\subsection{Ten}\label{ten}

\paragraph{Books Mentioned:}\label{books-mentioned-24}

\begin{itemize}
\tightlist
\item
  \emph{Unknown volume of The Catholic Encyclopedia}.
\item
  De Góngora Y Argote, Luis. \emph{The Solitudes of Luis De Góngora}. 1968.
\item
  \textbf{Kraft, Fellowes. \emph{Bitten Apples}}
\end{itemize}

\paragraph{Authors Mentioned:}\label{authors-mentioned-18}

John Dee, Giordano Bruno, Origen, Descartes, Peter Ramus, Francis Bacon.

\section{Bibliography by Author}\label{bibliography-by-author}

In the following bibliography duplicates have been removed unless they specifically are referring to a separate volume within the text. The foot notes from above are preserved as some are still pertinent.

\begin{itemize}
\tightlist
\item
  Agrippa, Heinrich Cornelius. \emph{De Occulta Philosophia}. 1533
\item
  al-Hakīm, Ghāyat. \emph{Picatrix}.
\item
  Apuleius. \emph{The Golden Ass}. 158-180.
\item
  ---. \emph{The Golden Ass}. Penguin UK, 1998.
\item
  \textbf{Barr, Frank Walker. \emph{Time's Body}.}
\item
  \textbf{---. \emph{Mythos and Tyrannos}.}
\item
  \textbf{---. Unnamed collected works of histories.}
\item
  Bates, Lizzie. \emph{Stories of the Flowers}. 1872.
\item
  Beeson, Charles H. ``A History of Magic and Experimental Science During the First Thirteen Centuries of Our Era. Lynn Thorndyke.'' \emph{Classical Philology}, vol.~20, no. 2, Apr.~1925, pp.~163--67. https://doi.org/10.1086/360664.
\item
  Benians, Ernest Alfred. \emph{The Cambridge Modern History}. Cambridge\,: UP, 1907.
\item
  Bruno, Giordano. \emph{Ars Memoriae}. 1582.
\item
  ---. \emph{De monade, numero et figura}. 1961.
\item
  ---. \emph{De umbris idearum}. 1582.
\item
  ---. \emph{Opera Omnia}. 1854.
\item
  ---. \emph{Jordani Bruni Opera Latine Conscripta}. 1962.
\item
  Briggs, Austin. \emph{Flash Gordon}. 1940-1948.
\item
  Burnett, Frances Hodgson, and Sue Ullstein. \emph{The Secret Garden}. Longman Publishing Group, 1975.
\item
  Burgess, Thornton W. \emph{Old Mother West Wind}. Courier Corporation, 2012.\footnote{Mentioned by Crowley as ``Old Mother Westwind''}
\item
  Cecco of Ascoli. \emph{Commentary on the Sphere}.1250.
\item
  Copernicus, Nicolaus. \emph{De Revolutionibus Orbium Coelestium}. 1543.
\item
  Dante. \emph{Divine Comedy}. Modern Library. 1950
\item
  Davidson, Gustav. \emph{A Dictionary of Angels\,: Incl. The Fallen Angels}. 1971.\footnote{While this is not named outright and is simply referred to as ``a dictionary of angels'' it is by far the most famous published prior to the 1980s and is likely the one Crowley was referring to.}
\item
  \emph{Das Nibelungenlied: Song of the Nibelungs}. Yale UP, 2006.
\item
  \textbf{\emph{Dawn of the Druids}.}
\item
  **\emph{Death's dream kingdom}''. Unknown Poem.\footnote{This must refer to T. S. Eliot's ``The Hollow Men'' from~\emph{Poems, 1909--1925}~(Faber \& Faber Limited, 1925).}
\item
  Dee, John. \emph{Monas hieroglyphica}. Antwerp, 1564.
\item
  ---. \emph{Propædeumata Aphoristica Ioannis Dee, Londinensis, De Præstantioribus Quibusdam Naturæ Virtutibus}. 1568.
\item
  \emph{De Góngora Y Argote, Luis. }The Solitudes of Luis De Góngora*. 1968.\footnote{Crowley quotes Cunningham's translation of the First Solitude lines 94-96 and then 108-111, then 112-116. Then he switches to the original Spanish for pieces of lines 113-114, and then again the Spainish for lines 119-121.}
\item
  **Faraway Crier*.**
\item
  Ficcino, Marsilio. \emph{De vita coelitis comparanda}.
\item
  ---. \emph{Pimander}. 1543.\footnote{Klutstein, Ilana. ``Ficino's Hermetic Translations: English Translation of His Latin Pimander.'' \emph{Huji}, Feb.~2017, www.academia.edu/31423671/Ficinos\_Hermetic\_Translations\_English\_Translation\_of\_His\_Latin\_Pimander.}
\item
  Fludd, Robert. \emph{Unnamed book}.\footnote{This can only mean Fludd's~\emph{Utriusque Cosmi}, however, there were no publications in english prior to the late 20th century. I believe it is instead referring to the following, but there will never be a way to tell for certain. (Paracelsus.~\emph{The Hermetic and Alchemical Writings of Aureolus Philippus Theophrastus Bombast, of Hohenheim, Called Paracelsus the Great}. 1894.)}
\item
  Frazer, James George. \emph{The Golden Bough: A Study in Magic and Religion}. 1932.
\item
  Herbermann, Charles George. \emph{The Catholic Encyclopedia: An International Work of Reference on the Constitution, Doctrine, Discipline, and History of the Catholic Church}. 1908.
\item
  Holinshed, Raphael. \emph{Holinshed's Chronicals: Richard II, 1398-1400, Henry IV and Henry V.} 1923.
\item
  Horapollo. \emph{Hieroglyphica}. \textasciitilde1419.
\item
  Huizinga, J. \emph{The Waning of the Middle Ages: A Study of the Forms of Life, Thought and Art in France and The Netherlands in the XIVth and XVth Centuries}. Pickle Partners Publishing, 2016.
\item
  Hyginus. \emph{Poeticon Astronomicon}. 1502.
\item
  Iambilichus. \emph{On the Mysteries of the Egyptians}.
\item
  ---. \emph{On the Mysteries of the Egyptians}.
\item
  \textbf{Kraft, Fellowes. \emph{A Passage at Arms}.}
\item
  \textbf{---. \emph{Bitten Apples}}
\item
  \textbf{---. \emph{Bitten Apples}}\footnote{This was Kraft's first book.}
\item
  \textbf{---. \emph{Bruno's Journey}. 1931}
\item
  \textbf{---. \emph{Darkling Plain}.}
\item
  \textbf{---. \emph{Darkling Plain}.}
\item
  \textbf{---. \emph{Sit Down, Sorrow}.}\footnote{A memoir of Fellowes Kraft.}
\item
  \textbf{---. \emph{The Book of a Hundred Chapters}.}
\item
  \textbf{---. \emph{The Borrowers Abroad}.}\footnote{There is no novel by Norton titled~\emph{The Borrowers Abroad}. This may have been deliberate by Crowley, or an accident, since all of the books are named in a similar pattern (i.e.~\emph{The Borrowers Afield},~\emph{The Borrowers Afloat},~\emph{The Borrowers Afield},~\emph{The Borrowers Avenged}. More research could be done to see if this was a proposed title of another book in the series, or if this was a subtle way to shift the book away from the reality, or history in this case, that we experience as the reader.)}
\item
  \textbf{---. \emph{The Court of Silk and Blood}.}
\item
  \textbf{---. \emph{Under Saturn, A Novel of Wallenstein}.}\footnote{Seems to be based on the biography of Wallenstein: Watson, Francis.~\emph{Wallenstein, Soldier Under Saturn}. 1969.}
\item
  \textbf{---. \emph{Under Saturn}.}
\item
  \textbf{---. \emph{Unfinished Final Novel}.}
\item
  Lanier, Sidney and Wyeth, N. C., Illustrator. \emph{The Boy's King Arthur. Scribner's Illustrated Classics. Sir Thomas Malory's History of King Arthur and His Knights of the Round Table}. Charles Scribner's Sons. 1937.
\item
  Lewis, Charlton T. \emph{Lewis and Short Latin Dictionary}. 1966.
\item
  Longfellow, Henry Wadsworth. \emph{The Golden Legend}. 1878.
\item
  Lull, Ramón. \emph{Ars Magna}. 1501.
\item
  Magus, Saint Albertus. \emph{Book of Secrets}.
\item
  ---. \emph{Commentaries on The ``Summa Theologica''}.
\item
  ---. \emph{On Sleeping and Being Awake}.
\item
  Malory, Thomas, and Sidney Lanier. \emph{The Boy's King Arthur: Being Sir Thomas Malory's History of King Arthur and His Knights of the Round Table}. 1921.
\item
  ---. \emph{Le Morte Darthur: The Winchester Manuscript}. Oxford UP, USA, 1998.
\item
  Mead, G.R.S. \emph{Thrice-greatest Hermes}. London and Benares. 1906.
\item
  Miss Martha's History Book\footnote{A completely unnamed history book belonging to Miss Martha, Pierce's uncle Sam's Houskeeper.}
\item
  Monardes, Nicolás. \emph{Joyfull Newes Out of the Newe Founde Worlde}. Walter J. Johnson Incorporated, 1970.
\item
  \textbf{Niblick, Helen. \emph{The Way's Far Turning}.}
\item
  \textbf{Norton, Mary. \emph{The Borrowers Abroad}.}
\item
  \emph{ORPHIC HYMNS 1-40 - Theoi Classical Texts Library}. www.theoi.com/Text/OrphicHymns1.html.
\item
  \textbf{\emph{Phaeton's Car}.}\footnote{Fictitious book apparently a play on Francis Bacon's~\emph{Of Vicissitude of Things}~``Phaeton's car went but a day: and the three years drought in the time of Elias, was but particular, and left people alive.'' Para. 60.}
\item
  Plutarch and North, Thomas, Sir. \emph{Lives. Englished}. London Dent. 1894.
\item
  \textbf{Rose, Lois. \emph{Steganography}.}
\item
  Seneschal, Jean Le, and Gaston Raynaud. \emph{Les Cent Ballades\,: Poème Du XIV{[}E{]} Siècle}. 1905, p221.
\item
  Shakespeare, William. \emph{Measure for Measure}. Cambridge UP, 2006.
\item
  ---. \emph{Shakespeare's King Henry VIII}. 1912.
\item
  ---. \emph{Unknown volumes of the Yale Shakespeare}
\item
  Sidney, Phillip, Sir. \emph{The Lady of May}. 1598.
\item
  Solomon. \emph{Shadows of Ideas}.\footnote{I have no idea what this is referring to.}
\item
  Spenser, Edmund. \emph{The Faerie Queene}. CUP Archive, 1920.
\item
  Sprat, Thomas. \emph{The History of the Royal Society of London, for the Improving of Natural Knowledge}. 1667.
\item
  Stedman, Joseph F. \emph{My Sunday Missal: Using New Translation From New Testament and a Simplified Method of Following Mass With an Explanation Before Each Mass of Its Theme}. Confraternity of the Precious Blood, 1961.\footnote{Title given in Aegypt is~\emph{Our Sunday Missal}~which could have been a misremembering of Crowley's part, or another slight alteration of the book's world from our own. Either way, this is the closest thing I can see Pierce having on his shelf.}
\item
  \textbf{Talbot's Unnamed Enochian Manuscript}*\footnote{Crowley mentions that ``Talbot'' aka Edward Kelley ``It was a manuscript on thick parchment, narrow and sewn up with heavy greased black thread. There was no cover or binding. The characters it was written in started immediately at the top of the first page without any heading, as though this were perhaps not the first page at all. Doctor Dee picked up the lamp and bent close over the page. Mr.~Talbot turned the heavy worm-holed leaf. The second page was the same: a solid block of characters from top to bottom. It is in a cipher, the doctor said. I can read a cipher, if it hides a language that I know.''}
\item
  Thomas, Saint. \emph{The ``Summa Theologica'' of St.~Thomas Aquinas}. 1917.
\item
  Trithemius, Johann. \emph{Johannis Trithemii \ldots{} Steganographia\ldots Illustrata a Wolfgango Ernesto Heidel}. 1676.
\item
  \emph{TV Guide}.
\item
  \emph{Unnamed Bible}.
\item
  \emph{Unnamed Big Dictionary}.
\item
  \emph{Unnamed Big Picture Book of Clocks}.\footnote{There are a few possibilities here as to what this books could have been. I'm simply going to list the most likely candidates here: ``The Book of Clocks'' by David Thompson (1971), ``Clocks and Watches'' by Eric Bruton (1973), ``The Art of the Clockmaker'' by Tardy (early 1970s), ``The Lore of the Clock'' by G. H. Baillie (1973).}
\item
  \emph{Unnamed Children's Book}.\footnote{I spent way too much time trying to track this book down. As best I can tell, there is no surviving children's ``book about the family of mice who go traveling in a balloon'' that was published in 1978 or before.}
\item
  \emph{Unnamed Mr.~Moto novel by John P. Marquand}.
\item
  \emph{Unnamed Nancy Drew Mystery Stories Novel}.
\item
  \emph{Unnamed Astronomy Textbook}
\item
  \emph{Unknown Big Bible}.
\item
  \emph{Unknown Big Shakespeare}.
\item
  \emph{Unknown Volumes of The Catholic Encyclopedia}.
\item
  \emph{Unknown Volumes of Encyclopedia Britannica}. 1939.\footnote{I am assuming the 1939 edition since Pierce mentions bringing several volumes of this fictitious version with him to Blackberry Jams.}
\item
  \emph{Unknown Volumes of Encyclopedia Britannica}. 1939.\footnote{The Encyclopedia Britannica became the first encyclopedia to undergo continual revisions in 1933. Crowley mentions ``Several volumes of the 1939 edition'' in this chapter, but there was not a specific edition published that year and as such it is impossible to easily tell what volumes of the 1933 14th edition were reprinted during 1939 specifically. Again this could be either intentional by Crowley subtly showing the differences between our world and the book's, or he simply could have chosen a date. Personally, I think it is likely the former.}
\item
  Virgil. \emph{Virgil's Eclogues}. University of Pennsylvania Press. 2011.\footnote{Line 6, ``Iam redit et Virgo, redeunt Saturnia regna'' ``The virgin reappears and Saturn reigns'' https://la.wikisource.org/wiki/Eclogae\_vel\_bucolica/Ecloga\_IV}
\end{itemize}

\section{Complete List of Authors}\label{complete-list-of-authors}

\begin{itemize}
\tightlist
\item
  Aeschylus
\item
  Aleister Crowley
\item
  Antoine de la Faye
\item
  Aristotle
\item
  Cecco of Ascoli
\item
  Charles Dickens
\item
  Charles Godfrey Leland
\item
  Cicero
\item
  Copernicus
\item
  Thomas B. Costain
\item
  Cusanus - Nicholas of Cusa
\item
  Dante
\item
  E. A. Wallis Budge
\item
  Epicurus
\item
  Euripides
\item
  Francis Bacon
\item
  François Rabelais
\item
  Galileo Galilei
\item
  Gerardus Mercator
\item
  Giordano Bruno
\item
  Hermes Trismegistus
\item
  Homer
\item
  Iamblichus
\item
  Isaac Newton
\item
  Jean-François Champollion
\item
  Johannes Kepler
\item
  John Dee
\item
  Joseph Lincoln
\item
  Karl Marx
\item
  Kathleen Norris{[}\^{}42{]}
\item
  Lady Mary Wortley Montagu
\item
  Lactantius
\item
  Lucretius
\item
  Luis de Góngora
\item
  Mackenzie
\item
  Macdonald
\item
  Margaret Mead
\item
  Margaret Nofzinger
\item
  Marsilio Ficcino
\item
  Martin del Rio ``Delrio''
\item
  Mary Norton
\item
  Miguel de Cervantes
\item
  Origen
\item
  Paracelsus
\item
  Percy Bysshe Shelley
\item
  Peter Ramus
\item
  Plato
\item
  Plotinus
\item
  Polydore Virgil
\item
  Proclus
\item
  Pythagoras
\item
  René Descartes
\item
  Robert Fludd
\item
  Ross Lockbridge
\item
  Samuel Shellabarger
\item
  Sir Walter Scott
\item
  Sophocles
\item
  Thomas Aquinas
\item
  Thomas Babington Macaulay
\item
  Thomas Milton
\item
  Tycho Brahe
\item
  Virgil
\item
  William Shakespeare
\item
  Zoroaster
\end{itemize}

%%\backmatter
\end{document}
