% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Love \& Sleep Bibliography},
  pdfauthor={Brian Murphy},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Love \& Sleep Bibliography}
\author{Brian Murphy}
\date{May 23, 2025}

\begin{document}
\maketitle

\section{Introduction}\label{introduction}

This is an attempt at listing out the various authors and books
mentioned within the second volume of the Ægypt Tetralogy, \emph{Love \&
Sleep} by John Crowley. Fictitious authors and books have been placed in
\textbf{bold} typeface for easy identification.

\subsection{To the Reader}\label{to-the-reader}

\subsubsection{Authors Mentioned}\label{authors-mentioned}

Piero Camporesi, Caroline Walker Bynum, Caroline Oates, Earnon McMullen.

\subsubsection{Books Metioned}\label{books-metioned}

\begin{itemize}
\tightlist
\item
  Night Comes to the Cumberlands: A Biography of a Depressed Area
  (\citeproc{ref-Caudill1963}{Caudill 1963})
\item
  Giordano Bruno and the Embassy Affair (\citeproc{ref-Bossy1991}{Bossy
  1991})
\item
  The Defeat of the Spanish Armada
  (\citeproc{ref-Mattingly1969}{Mattingly 1969})
\item
  The Night Battles: Witchcraft and Agrarian Cults in the Sixteenth and
  Seventeenth Centuries (\citeproc{ref-Ginzburg1985}{Ginzburg 1985})
\item
  Rudolf II and His World: A Study in Intellectual History, 1576 - 1612
  (\citeproc{ref-Evans1973}{Evans 1973})
\item
  Eros and Magic in the Renaissance (\citeproc{ref-Culianu1987}{Culianu
  1987})
\end{itemize}

\subsection{Prologue}\label{prologue}

\subsubsection{Epigraph}\label{epigraph}

\begin{quote}
Thou wouldst not think how ill all's here about my heart.

--- Hamlet
\end{quote}

\newpage

\section{Part One - Genitor}\label{part-one---genitor}

\subsection{Chapter One}\label{chapter-one}

\subsubsection{Books Mentioned}\label{books-mentioned}

\begin{itemize}
\tightlist
\item
  {``Collier's''} (\citeproc{ref-1952b}{1952})
\item
  {``Look''} (\citeproc{ref-1952}{1952})
\item
  {``Our Sunday Visitor''} (\citeproc{ref-1952a}{1952})
\end{itemize}

\subsection{Chapter Two}\label{chapter-two}

\subsubsection{Authors Mentioned}\label{authors-mentioned-1}

Alexander Hamilton, Thomas E. Dewey.

\subsection{Chapter Three}\label{chapter-three}

\subsection{Authors Mentioned}\label{authors-mentioned-2}

John Dee.

\subsubsection{Books Mentioned}\label{books-mentioned-1}

\begin{itemize}
\tightlist
\item
  {``Collier's''} (\citeproc{ref-1952b}{1952})
\item
  Nancy Drew. Vol. unknown (\citeproc{ref-NancyDrew}{Adams et al.,
  n.d.})
\item
  Black Beauty (\citeproc{ref-Sewell1887}{Sewell 1887})
\item
  A Dictionary of Deities, Devils and Dæmons of Mankind
  (\citeproc{ref-St.Phalle}{St. Phalle, n.d.})
\item
  Cherry Ames (\citeproc{ref-WellsPre1952}{Wells and Tatham Pre-1952})
\end{itemize}

\subsection{Chapter Four}\label{chapter-four}

\subsubsection{Books Mentioned}\label{books-mentioned-2}

\begin{itemize}
\tightlist
\item
  {``Roads and Highways''} (\citeproc{ref-UnknownRH}{n.d.})\footnote{While
    I could not find a school reader prior to 1952 with this name, I did
    find one from 1941 called \emph{Streets and Roads},
    (\citeproc{ref-Gray1941}{Gray 1941}).}
\end{itemize}

\subsection{Chapter Five}\label{chapter-five}

\subsubsection{Authors Mentioned}\label{authors-mentioned-3}

\begin{itemize}
\tightlist
\item
  Augustine of Hippo.
\end{itemize}

\subsubsection{Books Mentioned}\label{books-mentioned-3}

\begin{itemize}
\tightlist
\item
  {``Guns and Ammo''} (\citeproc{ref-gunsnammo}{pre-1953})\footnote{While
    Crowley mentions \emph{Guns and Ammo} as the magazine that his
    cousin Boyd was reading in 1952, the actual magazine wasn't founded
    until 1958. Therefore, I've marked it as fictitious.}
\end{itemize}

\subsection{Chapter Six}\label{chapter-six}

\subsubsection{Books Mentioned}\label{books-mentioned-4}

\begin{itemize}
\tightlist
\item
  {``Esquire''} (\citeproc{ref-esquire}{pre-1952})
\end{itemize}

\subsection{Chapter Thirteen}\label{chapter-thirteen}

\subsubsection{Authors Mentioned}\label{authors-mentioned-4}

\textbf{Fellowes Craft}.

\subsubsection{Books Mentioned}\label{books-mentioned-5}

\begin{itemize}
\tightlist
\item
  \textbf{\emph{Little Enosh: Lost Among the Worlds}
  (\citeproc{ref-enosh}{n.d.})\footnote{It has been posited by others
    that this could have been inspired on Winsor McCay's \emph{Little
    Nemo in Slumberland} which ran from 1905 until 1927. The only
    problem with that being that Pierce recalls getting ``the new Little
    Enosh'' while he was a child. This could just be another instance of
    transplanting one work in time by Crowley, however.}}
\item
  \textbf{The Werewolf of Prague (\citeproc{ref-CraftW1}{Craft,
  n.d.-d})}
\end{itemize}

\subsection{Chapter Fourteen}\label{chapter-fourteen}

\subsubsection{Authors Mentioned}\label{authors-mentioned-5}

Giordano Bruno, \textbf{Fellowes Craft}.

\subsubsection{Books Mentioned}\label{books-mentioned-6}

\begin{itemize}
\tightlist
\item
  \textbf{Bitten Apples. (\citeproc{ref-Craft}{Craft, n.d.-b})}
\item
  \textbf{A Passage at Arms (\citeproc{ref-Crafta}{Craft, n.d.-a})}
\item
  \textbf{The Werewolf of Prague (\citeproc{ref-CraftW1}{Craft,
  n.d.-d})}
\item
  The Expulsion of the Triumphant Beast (\citeproc{ref-Bruno1964}{G.
  Bruno 1964})
\item
  \textbf{Bruno's Journey (\citeproc{ref-Craft1931}{Craft 1931})}
\item
  \textbf{The Winter King (\citeproc{ref-Craft1941}{Craft 1941})}
\item
  \textbf{Elizabethan People (\citeproc{ref-Craft1953}{Craft 1953})}
\item
  \textbf{Astray (\citeproc{ref-Craft1959}{Craft 1959})}
\item
  \textbf{Scream Bloody Murder (\citeproc{ref-Craft1939}{Craft 1939})}
\item
  \textbf{Skin Deep (\citeproc{ref-Craftb}{Craft, n.d.-c})}
\item
  \textbf{Sit down, Sorrow (\citeproc{ref-Craft1960}{Craft 1960})}
\item
  \textbf{{``Faraway Crier''} (\citeproc{ref-faraway}{n.d.})}
\end{itemize}

\subsection{Chapter Fifteen}\label{chapter-fifteen}

\subsubsection{Authors Mentioned}\label{authors-mentioned-6}

John Milton, Virgil, Dante.

\subsubsection{Books Mentioned}\label{books-mentioned-7}

\begin{quote}
``All night upon mine heart I felt her warm heart beat. Nightlong within
mine arms in love and sleep she lay.''

--- Ernest Christopher Dowson, \emph{``Cynara''}
\end{quote}

\begin{itemize}
\tightlist
\item
  \textbf{Time's Body (\citeproc{ref-Barr}{Barr, n.d.})}
\end{itemize}

\newpage

\section{Part Two - Nati}\label{part-two---nati}

\subsection{Chapter One}\label{chapter-one-1}

\subsubsection{Books Mentioned}\label{books-mentioned-8}

\begin{itemize}
\tightlist
\item
  The Triumphal Chariot of Antimony by Basilius Valentinus
  (\citeproc{ref-Valentinus.1893}{Valentinus., Kerckring, and Waite
  1893})
\item
  Amphitheatrum Sapientiae Aeternae, Solius Verae,
  Christiano-Kabalisticum, Divino-Magicum\ldots{}
  (\citeproc{ref-Khunrath1609}{Khunrath 1609})
\item
  Utriusque Cosmi\ldots{} Metaphysica, Physica Atque Technica\ldots{}
  (\citeproc{ref-Fludd1617}{Fludd 1617})
\item
  Recens Et Completa Ars Reminiscendi Et in Phantastico\ldots{}
  (\citeproc{ref-Bruno1583}{G. (. Bruno 1583})
\end{itemize}

\subsection{Chapter Three}\label{chapter-three-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-7}

Nicolaus Copernicus, Marsilio Ficino, Pythagoras, Marcellus Palingenius
Stellatus, Socrates.

\subsubsection{Books Mentioned}\label{books-mentioned-9}

\begin{itemize}
\tightlist
\item
  Monas Hieroglyphica\ldots{} (\citeproc{ref-Dee1564}{Dee 1564})
\end{itemize}

\subsection{Chapter Four}\label{chapter-four-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-8}

Aristotle, Nicolaus Copernicus, Marsilio Ficino, Samuel Daniel, Matthew
Gwynne (Gwinne), Plato, Pythagoras.

\subsection{Chapter Five}\label{chapter-five-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-9}

John Dee, Giordano Bruno, Méric Casaubon, Paracelsus.

\subsubsection{Books Mentioned}\label{books-mentioned-10}

\begin{itemize}
\tightlist
\item
  \textbf{Bruno's Journey (\citeproc{ref-Craft1931}{Craft 1931})}
\item
  A True \& Faithful Relation of What Passed for Many Yeers Between
  Dr.~John Dee \ldots{} And Some Spirits\ldots{}
  (\citeproc{ref-Dee1659}{Dee 1659})
\item
  John Dee 1527-1608 (\citeproc{ref-Smith1909}{Smith 1909})
\item
  Hypnerotomachia (\citeproc{ref-Colonna1592}{Colonna 1592})\footnote{Crowley
    mentions that it is published in 1594, but it seems to actually have
    been 1592.}
\end{itemize}

\subsection{Chapter Six}\label{chapter-six-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-10}

Hildegard of Bingen OSB, Oswald Croll, Cornelius Drebbel, Johannes
Kepler, Jöst Burgi.

\subsubsection{Books Mentioned}\label{books-mentioned-11}

\begin{itemize}
\tightlist
\item
  Unknown Guidebook to Prague (\citeproc{ref-UnknownPre1967}{Unknown
  Pre-1967})
\item
  Osvaldi Crollii Veterani Hassi Basilica Chymica: Continens.
  Philosophicam Propria Laborum Experientia Confirmatam Descriptionem Et
  Usum Remediorum Chymicorum Selectissimorum e Lumine Gratiae Et Naturae
  Desumptorum (\citeproc{ref-Croll1611}{Croll 1611})
\end{itemize}

\subsection{Chapter Seven}\label{chapter-seven}

\subsubsection{Authors Mentioned}\label{authors-mentioned-11}

Diotima of Mantinea\footnote{See Plato's Symposium
  (\citeproc{ref-Plato1925}{Plato 1925}).}.

\subsubsection{Books Mentioned}\label{books-mentioned-12}

\begin{itemize}
\tightlist
\item
  A Dictionary of Deities, Devils and Dæmons of Mankind
  (\citeproc{ref-St.Phalle}{St. Phalle, n.d.})\footnote{While not stated
    by name, the book that Val begins reading to Rosie is undoubtedly
    the same which Pierce had as a boy.}
\end{itemize}

\subsection{Chapter Eight}\label{chapter-eight}

\subsubsection{Authors Mentioned}\label{authors-mentioned-12}

Johannes Virdung, Robert Burton.

\subsubsection{Books Mentioned}\label{books-mentioned-13}

\begin{itemize}
\tightlist
\item
  Hypnerotomachia (\citeproc{ref-Colonna1592}{Colonna 1592})
\item
  De Cognoscendis, Et Medendis Morbis Ex Corporum Coelestium Positione
  Libri Quattuor (\citeproc{ref-Virdung1584}{Virdung 1584})\footnote{Only
    alluded to in Nati-8, by mention of the author Johannes Virdung but
    this is his only real work.}
\item
  The Anatomy of Melancholy: What It Is ; with All the Kinds, Causes,
  Symptoms, Prognostics, and Several Cures of It ; in Three Partitions
  (\citeproc{ref-Burton1863}{Burton 1863})\footnote{Crowley mentions the
    Third Partition, Section II, Member I, Subsection I which contains a
    retelling of the tale of Venus' birth as reported to Socrates by
    Diotima and read by Val to Rosie in Nati-7.}\footnote{In this same
    section he has Pierce recognizing Giordano Bruno within the Third
    Partition, Section II, Member II, Subsection II. This section
    mentions the ``winds of love'' that Rosie Rasmussen refers to later
    in Nati-15.}
\end{itemize}

\subsection{Chapter Eight}\label{chapter-eight-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-13}

G.R.S. Mead.

\subsubsection{Books Mentioned}\label{books-mentioned-14}

\begin{itemize}
\tightlist
\item
  Thrice-Greatest Hermes: Studies in Hellenistic Theosophy and
  Gnosis\ldots{} (\citeproc{ref-Mead1906}{Mead 1906})
\end{itemize}

\subsection{Chapter Nine}\label{chapter-nine}

\subsubsection{Authors Mentioned}\label{authors-mentioned-14}

Plato.

\subsubsection{Books Mentioned}\label{books-mentioned-15}

\begin{itemize}
\tightlist
\item
  \textbf{A Dictionary of Deities, Devils and Dæmons of Mankind
  (\citeproc{ref-St.Phalle}{St. Phalle, n.d.})}
\item
  \textbf{\emph{Little Enosh: Lost Among the Worlds}
  (\citeproc{ref-enosh}{n.d.})\footnote{It has been posited by others
    that this could have been inspired on Winsor McCay's \emph{Little
    Nemo in Slumberland} which ran from 1905 until 1927. The only
    problem with that being that Pierce recalls getting ``the new Little
    Enosh'' while he was a child. This could just be another instance of
    transplanting one work in time by Crowley, however.}}
\item
  Dialogues of Plato: Translated into English, with Analyses and
  Introduction : Volume 1 (\citeproc{ref-Jowett1871}{Jowett 1871})
\end{itemize}

\subsection{Chapter Ten}\label{chapter-ten}

\subsubsection{Authors Mentioned}\label{authors-mentioned-15}

Dante Alighieri.

\subsection{Chapter Eleven}\label{chapter-eleven}

\subsubsection{Authors Mentioned}\label{authors-mentioned-16}

Annibale Roselli\footnote{Named by Crowley using the variant
  ``Dr.~Hannibal.''}, Joachim of Fiore\footnote{Named by Crowley as
  ``Abbot Joachim of Flora.''}, Heinrich Agrippa,

\subsubsection{Books Mentioned}\label{books-mentioned-16}

\begin{itemize}
\tightlist
\item
  Pymander Mercurii Trismegisti Cum Commento Hannibalis Rosseli
  (\citeproc{ref-Rosselli1585}{Rosselli 1585})
\item
  De Occulta Philosophia (\citeproc{ref-Nettesheim1565}{Heinrich
  Cornelius Agrippa von Nettesheim 1565})
\item
  Monas Hieroglyphica Ioannis Dee (\citeproc{ref-Dee1564}{Dee 1564})
\end{itemize}

\subsection{Chapter Twelve}\label{chapter-twelve}

\subsubsection{Authors Mentioned}\label{authors-mentioned-17}

Giordano Bruno.

\subsubsection{Books Mentioned}\label{books-mentioned-17}

\begin{itemize}
\tightlist
\item
  Iordanvs Brvnvs Nolanvs de Vmbris Idearvm\ldots{}
  (\citeproc{ref-Bruno1582}{G. Bruno 1582})
\end{itemize}

\subsection{Chapter Thirteen}\label{chapter-thirteen-1}

\subsubsection{Books Mentioned}\label{books-mentioned-18}

\begin{itemize}
\tightlist
\item
  Dictionary of American Biography
  (\citeproc{ref-LearnedSocieties1943}{American Council of Learned
  Societies 1943-})
\item
  \textbf{Climacterics: Your New Ancient Guide to Life's Cycles
  (\citeproc{ref-Muchon.d}{Mucho n.d.})}\footnote{A book title made up
    by Pierce to Rose Ryder.}
\end{itemize}

\subsection{Chapter Fourteen}\label{chapter-fourteen-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-18}

\textbf{Fellowes Kraft}.

\subsubsection{Books Mentioned}\label{books-mentioned-19}

\begin{itemize}
\tightlist
\item
  \textbf{Sit down, Sorrow (\citeproc{ref-Craft1960}{Craft 1960})}
\end{itemize}

\newpage

\section{Part Three - Valetudo}\label{part-three---valetudo}

\subsection{Chapter One}\label{chapter-one-2}

\subsubsection{Authors Mentioned}\label{authors-mentioned-19}

\textbf{Fellowes Kraft}.

\subsubsection{Books Mentioned}\label{books-mentioned-20}

\begin{itemize}
\tightlist
\item
  \textbf{Ill Met by Moonlight (\citeproc{ref-KraftIll}{Kraft,
  n.d.})}\footnote{Noted as being a book of ghost stories by Fellowes
    Kraft.}
\item
  Unknown Bible\footnote{The bible is used by the pastor at Boney's
    funeral where Job 1:21 is quoted. As an aside this led to a look
    into the possible origins of the particular denomination that Boney
    belonged to, here named ``The Danish Brethren.'' The best I can
    determine now is that it was a splinter group formed after the first
    or second schism of the Bible Student Movement in the late 1920s,
    prior to gaining the name Jehovah's Witnesses.}
\end{itemize}

\subsection{Chapter Two}\label{chapter-two-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-20}

Plato, Shakespeare, Giordano Bruno.

\subsection{Chapter Three}\label{chapter-three-2}

\subsubsection{Authors Mentioned}\label{authors-mentioned-21}

Alexander Dicson, Albertus, Aquinas, Triptolemus, Euclid, Copernicus,
John Dee, Paracelsus.

\subsubsection{Books Mentioned}\label{books-mentioned-21}

\begin{itemize}
\tightlist
\item
  \textbf{Faraway Crier (\citeproc{ref-faraway}{{``Faraway Crier,''}
  n.d.})}
\item
  \textbf{A Dictionary of Deities, Devils and Dæmons of Mankind
  (\citeproc{ref-St.Phalle}{St. Phalle, n.d.})}
\item
  De umbra rationis \& judicii (\citeproc{ref-Dicson1584}{Dicson 1584})
\item
  AVREOLI THEOPHRA Seu de Secretis Naturae mysteriis\ldots{}
  (\citeproc{ref-Paracelsus1582}{Paracelsus 1582})
\end{itemize}

\subsection{Chapter Four}\label{chapter-four-2}

\subsubsection{Authors Mentioned}\label{authors-mentioned-22}

John Dee, Euclid.

\subsubsection{Books Mentioned}\label{books-mentioned-22}

\begin{itemize}
\tightlist
\item
  Monas Hieroglyphica Ioannis Dee, Londinensis, Ad Maximilianvm, Dei
  Gratia Romanorvm, Bohemiæ Et Hvngariæ Regem Sapientissimvm
  (\citeproc{ref-Dee1564}{Dee 1564})
\item
  Steganographia (\citeproc{ref-Trithemius1608}{Trithemius 1608})
\end{itemize}

\subsection{Chapter Six}\label{chapter-six-2}

\subsubsection{Book Mentioned}\label{book-mentioned}

\begin{itemize}
\tightlist
\item
  \textbf{Faraway Crier (\citeproc{ref-faraway}{{``Faraway Crier,''}
  n.d.})}
\end{itemize}

\subsection{Chapter Seven}\label{chapter-seven-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-23}

Nostradamus, Regiomontanus, Cornelius Drebbel, John Dee.

\subsubsection{Book Mentioned}\label{book-mentioned-1}

\begin{itemize}
\tightlist
\item
  Sphaera mundi (\citeproc{ref-JSB1490}{Johannes de Sacro Busto 1490})
\end{itemize}

\subsection{Chapter Eight}\label{chapter-eight-2}

\subsubsection{Books Mentioned}\label{books-mentioned-23}

\begin{itemize}
\tightlist
\item
  National Geographic (\citeproc{ref-natgeo}{{``National Geographic,''}
  n.d.})
\end{itemize}

\subsection{Chapter Nine}\label{chapter-nine-1}

\subsubsection{Authors Mentioned}\label{authors-mentioned-24}

Marsilio Ficino, Dante, Petrarch, Robert Burton.

\subsubsection{Books Mentioned}\label{books-mentioned-24}

\begin{itemize}
\tightlist
\item
  De vita coelitus comparanda (\citeproc{ref-Ficino1560}{Ficino 1560})
\item
  The Anatomy of Melancholy (\citeproc{ref-Burton1863}{Burton
  1863})\footnote{Pierce never mentions the book by name here but
    instead by Burton's name and references \emph{``Amor hereos''} which
    Barr says \emph{``\ldots was a part of melancholy.''}}
\end{itemize}

\newpage

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-NancyDrew}
Adams, Harriet Stratemeyer, Edward Stratemeyer, Edna Stratemeyer Squier,
and Harriet Otis Smith. n.d. \emph{Nancy Drew}. Vol. unknown. Nancy Drew
Mystery Stories. Simon; Schuster.

\bibitem[\citeproctext]{ref-LearnedSocieties1943}
American Council of Learned Societies. 1943-. \emph{Dictionary of
American Biography}. Dictionary of American Biography. C. Scribner's
Sons, New York.

\bibitem[\citeproctext]{ref-Barr}
Barr, Frank Walker. n.d. \emph{Time's Body}.

\bibitem[\citeproctext]{ref-Bossy1991}
Bossy, John. 1991. \emph{Giordano Bruno and the Embassy Affair}. New
Haven, Conn. {[}u.a.{]}: Yale Univ. Press.

\bibitem[\citeproctext]{ref-Bruno1582}
Bruno, Giordano. 1582. \emph{Iordanvs Brvnvs Nolanvs de Vmbris Idearvm:
Implicantibus Artem, Quaetendi, Inueniendi, Iudicandi, Ordinandi, \&
Applicandi ... Ad Henricvm III. ... Gallor. Polonorumque Regem \&c.
Protestatio}. Parisiis: Gorbin.

\bibitem[\citeproctext]{ref-Bruno1964}
---------. 1964. \emph{The Expulsion of the Triumphant Beast}. Edited by
Arthur D. Imerti. Rutgers University Press.

\bibitem[\citeproctext]{ref-Bruno1583}
Bruno, Giordano (. 1583. {``Philothei Jordani Bruni Nolani Recens Et
Completa Ars Reminiscendi Et in Phantastico Campo Exarandi Ad Plurimas
in Triginta Sigillis Inquirendi, Disponendi, Atque Retinendi Implicitas
Novas Rationes \& Artes Introductoria.''}

\bibitem[\citeproctext]{ref-Burton1863}
Burton, Robert. 1863. \emph{The Anatomy of Melancholy: What It Is ; with
All the Kinds, Causes, Symptoms, Prognostics, and Several Cures of It ;
in Three Partitions ...} A new ed. London: Tegg.

\bibitem[\citeproctext]{ref-Caudill1963}
Caudill, Harry M. 1963. \emph{Night Comes to the Cumberlands: A
Biography of a Depressed Area}. Edited by Stewart L. Udall. Boston
{[}u.a.{]}: Little, Brown.

\bibitem[\citeproctext]{ref-1952b}
{``Collier's.''} 1952. Print, weekly.

\bibitem[\citeproctext]{ref-Colonna1592}
Colonna, Francesco. 1592. \emph{Hypnerotomachia}. Edited by null null
and Robert Dallington. Early English Books Online / EEBO. At London:
Printed {[}by Abell Jeffes, John Charlewood,; Eliot's Court Press{]} for
Simon VVaterson,; are to be sold at his shop, in S. Paules Church-yard,
at Cheape-gate.

\bibitem[\citeproctext]{ref-Crafta}
Craft, Fellowes. n.d.-a. \emph{A Passage at Arms}.

\bibitem[\citeproctext]{ref-Craft}
---------. n.d.-b. \emph{Bitten Apples}.

\bibitem[\citeproctext]{ref-Craftb}
---------. n.d.-c. \emph{Skin Deep}. Herm Press.

\bibitem[\citeproctext]{ref-CraftW1}
---------. n.d.-d. \emph{The Werewolf of Prague}.

\bibitem[\citeproctext]{ref-Craft1931}
---------. 1931. \emph{Bruno's Journey}.

\bibitem[\citeproctext]{ref-Craft1939}
---------. 1939. \emph{Scream Bloody Murder}.

\bibitem[\citeproctext]{ref-Craft1941}
---------. 1941. \emph{The Winter King}.

\bibitem[\citeproctext]{ref-Craft1953}
---------. 1953. \emph{Elizabethan People}.

\bibitem[\citeproctext]{ref-Craft1959}
---------. 1959. \emph{Astray}.

\bibitem[\citeproctext]{ref-Craft1960}
---------. 1960. \emph{Sit down, Sorrow}.

\bibitem[\citeproctext]{ref-Croll1611}
Croll, Oswald. 1611. \emph{Osvaldi Crollii Veterani Hassi Basilica
Chymica: Continens. Philosophicam Propria Laborum Experientia
Confirmatam Descriptionem Et Usum Remediorum Chymicorum Selectissimorum
e Lumine Gratiae Et Naturae Desumptorum}. Edited by Johann Hartmann,
null null, and Petrus Wok Ursinus a Rosenberg. Francofurti: Tampachius.

\bibitem[\citeproctext]{ref-Culianu1987}
Culianu, Ioan P. 1987. \emph{Eros and Magic in the Renaissance}. Edited
by Margaret Cook and Mircea Eliade. Chicago, Ill. {[}u.a.{]}: Univ. of
Chicago Press.

\bibitem[\citeproctext]{ref-Dee1564}
Dee, John. 1564. \emph{Monas Hieroglyphica Ioannis Dee, Londinensis, Ad
Maximilianvm, Dei Gratia Romanorvm, Bohemiæ Et Hvngariæ Regem
Sapientissimvm}. Edited by null null and Willem Silvius. Antverpiae:
Silvius.

\bibitem[\citeproctext]{ref-Dee1659}
---------. 1659. \emph{A True \& Faithful Relation of What Passed for
Many Yeers Between Dr. John Dee ... And Some Spirits: Tending ... To a
General Alteration of Most States and Kingdomes in the World : His
Private Conferences with Rodolphe, Emperor of Germany, Stephen, k. Of
Poland, and Divers Other Princes about It ... : As Also the Letters of
Sundry Great Men and Princes ... To the Said d. Dee}. Edited by Meric
Casaubon and Edward Kelly. Early English Books Online / EEBO. London:
Printed by D. Maxwell for T. Garthwait.

\bibitem[\citeproctext]{ref-Dicson1584}
Dicson, Alexander. 1584. \emph{De Umbra Rationis \& Judicii}.

\bibitem[\citeproctext]{ref-esquire}
{``Esquire.''} pre-1952. Print.

\bibitem[\citeproctext]{ref-Evans1973}
Evans, Robert John Weston. 1973. \emph{Rudolf II and His World: A Study
in Intellectual History, 1576 - 1612}. Oxford: Clarendon Press.

\bibitem[\citeproctext]{ref-faraway}
{``Faraway Crier.''} n.d.

\bibitem[\citeproctext]{ref-Ficino1560}
Ficino, Marsilio. 1560. \emph{Marsilii {Ficini} ... {De} Vita Libri
Tres, Recèns Iam à Mendis Situque Vindicati, Ac Summa Castigati
Diligentia, 1. {De} Studiosorum Sanitate Tuenda. 2. {De} Vita
Producenda. 3. {De} Vita Coelitus Comparanda}. apud Gulielmum Rouillium
sub scuto Veneto. \url{http://archive.org/details/bub_gb_buTQ-hAMvw0C}.

\bibitem[\citeproctext]{ref-Fludd1617}
Fludd, Robert (. 1617. {``Utriusque Cosmi... Metaphysica, Physica Atque
Technica... Authore Roberto Flud, Aliàs de Fluctibus... Tomus Is...''}

\bibitem[\citeproctext]{ref-Ginzburg1985}
Ginzburg, Carlo. 1985. \emph{The Night Battles: Witchcraft and Agrarian
Cults in the Sixteenth and Seventeenth Centuries}. New York: Penguin.

\bibitem[\citeproctext]{ref-Gray1941}
Gray, William Scott. 1941. \emph{Streets and Roads}. Basic Readers 1.
Scott, Foresman; Company.

\bibitem[\citeproctext]{ref-gunsnammo}
{``Guns and Ammo.''} pre-1953.

\bibitem[\citeproctext]{ref-Nettesheim1565}
Heinrich Cornelius Agrippa von Nettesheim. 1565. \emph{HENRICI
\textbar\textbar{} CORNELII AGRIP-\textbar\textbar PAE LIBER QVARTVS
\textbar\textbar{} DE OCCVLTA PHI-\textbar\textbar Losophia, Seu de
Ceri-\textbar\textbar Monijs
Ma-\textbar\textbar Gicis.\textbar\textbar{} Cui Accesserunt, Elementa
\textbar\textbar{} Magica Petri de Abano,\textbar\textbar{}
Philosophi.\textbar\textbar{}}. Edited by null null. Köln: Birckmann,
Johann.

\bibitem[\citeproctext]{ref-JSB1490}
Johannes de Sacro Busto. 1490. \emph{Sphaera Mundi. {Add}: {Georgius}
{Purbachius}: {Theoricae} Novae Planetarum. {Regiomontanus}:
{Disputationes} Contra {Cremonensia} Deliramenta}. Locatelli, Boneto,
fl. 1486-1523.
\url{http://archive.org/details/ita-bnc-in1-00000496-001}.

\bibitem[\citeproctext]{ref-Jowett1871}
Jowett, Benjamin, ed. 1871. \emph{Dialogues of Plato: Translated into
English, with Analyses and Introduction : Volume 1}. Cambridge Library
Collection. Classics. Place of publication not identified: publisher not
identified.

\bibitem[\citeproctext]{ref-Khunrath1609}
Khunrath, Heinrich. 1609. \emph{Amphitheatrum Sapientiae Aeternae,
Solius Verae, Christiano-Kabalisticum, Divino-Magicum, Nec Non
Physico-Chymicum, Tertriunum, Catholicon}. Edited by Erasmus Wolfart and
A. Benck. Hanoviae: Antonius.

\bibitem[\citeproctext]{ref-KraftIll}
Kraft, Fellowes. n.d. \emph{Ill Met by Moonlight}.

\bibitem[\citeproctext]{ref-enosh}
\emph{Little Enosh: Lost Among the Worlds}. n.d.

\bibitem[\citeproctext]{ref-1952}
{``Look.''} 1952. print, bi-weekly.

\bibitem[\citeproctext]{ref-Mattingly1969}
Mattingly, Garrett. 1969. \emph{The Defeat of the Spanish Armada}. 7.
impr. London: Cape.

\bibitem[\citeproctext]{ref-Mead1906}
Mead, George Robert Stow. 1906. \emph{Thrice-Greatest Hermes: Studies in
Hellenistic Theosophy and Gnosis Being a Transl. Of the Extant Sermons
and Fragments of the Trismegistic Literature, with Prolegomena,
Commentaries and Notes by g{[}eorge{]} r{[}obert{]} s{[}tow{]} Mead}.
London \& Benares: Theos. Publ. Soc.

\bibitem[\citeproctext]{ref-Muchon.d}
Mucho, Mike. n.d. \emph{Climacterics: Your New Ancient Guide to Life's
Cycles}.

\bibitem[\citeproctext]{ref-natgeo}
{``National Geographic.''} n.d.

\bibitem[\citeproctext]{ref-1952a}
{``Our Sunday Visitor.''} 1952. Print, weekly newspaper.

\bibitem[\citeproctext]{ref-Paracelsus1582}
Paracelsus. 1582. \emph{AVREOLI THEOPHRA Seu de Secretis Naturae
Mysteriis...} Basel: Perna, Peter.

\bibitem[\citeproctext]{ref-Plato1925}
Plato. 1925. \emph{Lysis ; Symposium ; Gorgias}. Edited by Martin
Schanz. Translated by W. R. M. Lamb. London, New York: William Heinemann
: G.P. Putnam's Sons.

\bibitem[\citeproctext]{ref-UnknownRH}
{``Roads and Highways.''} n.d.

\bibitem[\citeproctext]{ref-Rosselli1585}
Rosselli, Annibale, ed. 1585. \emph{Pymander Mercurii Trismegisti Cum
Commento Hannibalis Rosseli ... Liber Primus de SS. Trinitate}.
Cracoviae: Lazari.

\bibitem[\citeproctext]{ref-Sewell1887}
Sewell, Anna. 1887. \emph{Black Beauty}. Jarold \& Sons.

\bibitem[\citeproctext]{ref-Smith1909}
Smith, Charlotte Fell. 1909. \emph{John Dee
\textless1527-1608\textgreater{}}. London: Constable.

\bibitem[\citeproctext]{ref-St.Phalle}
St. Phalle, Alexis Payne de. n.d. \emph{A Dictionary of Deities, Devils
and Dæmons of Mankind}.

\bibitem[\citeproctext]{ref-Trithemius1608}
Trithemius, Johannes. 1608. \emph{Steganographia}.
\url{http://archive.org/details/SteganographiaBSB1608}.

\bibitem[\citeproctext]{ref-UnknownPre1967}
Unknown. Pre-1967. \emph{Unknown Guidebook to Prague}.

\bibitem[\citeproctext]{ref-Valentinus.1893}
Valentinus., Basilius, Theodor Kerckring, and Arthur Edward. Waite.
1893. {``The Triumphal Chariot of Antimony by Basilius Valentinus ; with
the Commentary of Theodore Kerckringius ; Being the Latin Version
Published at Amsterdam in the Year 1685, Translated into English, with a
Biographical Preface.''} J. Elliott,.
\url{https://doi.org/10.5962/bhl.title.26696}.

\bibitem[\citeproctext]{ref-Virdung1584}
Virdung, Johann. 1584. \emph{De Cognoscendis, Et Medendis Morbis Ex
Corporum Coelestium Positione Libri Quattuor}. Edited by Giovanni Paolo
Gallucci. Venetijs: Zenarius.

\bibitem[\citeproctext]{ref-WellsPre1952}
Wells, Helen, and Julie Campbell Tatham. Pre-1952. \emph{Cherry Ames}.
Vol. Unknown. Cherry Ames. Grosset \& Dunlop.

\end{CSLReferences}

\end{document}
